---
title: "homework0"
author: "Wanyue Dong"
format: html
editor: visual
---

## Plot

In the following plot section, I first assigned numbers to a,b,c (a=1,b=3,c=2) and created x to be a sequence of numbers between -5 and 5. Then I generated a graph by plotting the function $y=ax^2+bx+c$ and added a horizontal line at $y=0$ to show the solutions to $ax^2+bx+c=0$

```{r}
#| echo: false
a <- 1 
b <- 3
c <- 2
x <- seq(-5, 5, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
```

## Solutions

This section is finding the numeric solutions to $ax^2+bx+c=0$. I created a function called `f` with a,b,c as inputs. It returns 0, 1, or 2 solutions to the function. It is discriminated by whether $b^2-4ac$ is greater, equal, or less than 0. The solution is calculated by the function $\frac{-b\pm\sqrt{b^2-4ac}}{2a}$

-   if $b^2-4ac < 0$
    -   the function has 0 solution
-   if $b^2-4ac = 0$
    -   the function has exactly 1 solution
-   if $b^2-4ac > 0$
    -   the function has 2 solutions

```{r}
#| echo: false

f <- function(a,b,c){
  if ((b^2-4*a*c) < 0){
    return ("no solution")
  }
  else if ((b^2-4*a*c) == 0){
    return (-b/(2*a))
  }
  else {
    x1 <- (-b+sqrt(b^2-4*a*c))/(2*a)
    x2 <- (-b-sqrt(b^2-4*a*c))/(2*a)
    return (list(x1=x1,x2=x2))
  }
}

f(1,3,2)

```
In the case of $a=1,b=3,c=2$, the function has two solutions with $x_1 =-1, x_2 = -2$